Untwisting the Tetrahelix (v0.5)

### 2017-02-22 doc/TetrahelixUntwist.tex
d_opt corrected and checked

This formula defines a helix, but it is not any of the apparent helices, or rail helices, of the
BC helix, but rather one that winds three times as rapidly through all
nodes. To a designer of tetrahelices, it is more natural to think of
the three helices which are visually apparent, that is, those three
which are closely approximated by the by the outer edges or rails of
the BC helix.

It is convenient to have a formula that gives us the nodes of just
one rail helix, denoted by $c$:
\[
(\forall n \in \mathbb{Z}, \forall c \in \{0,1,2\} : H_{BCcolored}(n,c) = V(3n +c))
\]

@@

In this formula, integral values of $n$ may be taken as a node number for one rail and used to compute its Cartesian
coordinates. Allowing $n$ to take non-integer values defines a continuous
helix in space which is close to the segmented polyline of the outer tetrahedra edges, and coincides with them at integer
values.
The parameter $c \in \{0,1,2\}$ specifies which of the rails is being computed.

The quantity $ (3 \theta - 2 \pi) \approx 35.43 \degree $, and is the angular shift between $V(n,color)$ and
$V(n+1,color)$. This quantity appears so often below that we call it the ``rail angle rho''. For the BC helix, $\rho_{bc} = (3 \theta - 2 \pi)$.

@@

Note: $r_{opt} $ is not an even function. I think it is only valid for non-negative values of $\rho$, an issue
we must face when we build our continuum.
Note: $ d_{opt} $ is computed by $\rho, r_{opt}$ via the rail angle equation \eqref{railangle}.

\begin{align*}
  d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
  d_{opt}^2 &= 1 - \frac{32(\sin{ \rho / 2})^2}{9 ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
  d_{opt}^2 &= 1 - \frac{8 sin^2(\rho / 2) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
    d_{opt} &= \sqrt{1 - \frac{8 sin^2(\rho / 2) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
\end{align*}
NOTE: I may have made a terrible mistake here, I'm unsure if the numerator should have $sin^2(\rho)$ or $sin^2(\rho/2)$.

@@

The pitch of the resulting tetrahix 
where $\rho \neq 0$ is:
\[
p(\rho) = \frac{2 \pi  \cdot d_{opt}}{\rho}
\]

>>>>

This formula defines a helix, but it is not any of the apparent helices, or rail helices, of the
BC helix, but rather one that winds three times as rapidly through all
nodes. To a designer of tetrahelices, it is more natural to think of
the three helices which are visually apparent, that is, those three
which are closely approximated by the by the outer edges or rails of
the BC helix. We think of each of these three rails as being a different color, red, blue, or yellow.

It is convenient to have a formula that gives us the nodes of just
one rail helix, denoted by color $c$:
\[
(\forall n \in \mathbb{Z}, \forall c \in \{0,1,2\} : H_{BCcolored}(n,c) = V(3n +c))
\]

@@

In this formula, integral values of $n$ may be taken as a node number for one rail and used to compute its Cartesian
coordinates. Allowing $n$ to take non-integer values defines a continuous
helix in space which is close to the segmented polyline of the outer tetrahedra edges, and coincides with them at integer
values.

The quantity $ (3 \theta - 2 \pi) \approx 35.43 \degree $, and is the angular shift between $V(n*3+c)=H_{BCcolored}(n,c)$ and
$V((n+1)*3+c)=H_{BCcolored}(n+1,c)x$.
This quantity appears so often that we call it the ``rail angle rho''. For the BC helix, $\rho_{bc} = (3 \theta - 2 \pi)$.

@@

We can now give a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \eqref{railangle}:

\begin{align*}
  d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
  d_{opt}^2 &= 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
  d_{opt}^2 &= 1 - \frac{16 sin^2(\rho / 2) }{ cos(\rho) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
    d_{opt} &= \sqrt{1 - \frac{16 sin^2(\rho / 2) }{ cos(\rho) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
\end{align*}
NOTE: I may have made a terrible mistake here, I'm unsure if the numerator should have $sin^2(\rho)$ or $sin^2(\rho/2)$.

@@

The pitch of any tetrahelix 
where $\rho \neq 0$ is:
\[
p(\rho) = \frac{2 \pi  \cdot d}{\rho}
\]
